Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-09-07 Manuscript/manuscript.tex
Updated PC-PS interaction plots (now also contain 50:50 mix)
Removed the plot POPC w.r.t surfactant DHMDAB

Changes of the lipid bilayer head group order parameters extracted from simulations and 
experiments \cite{roux90} are shown in Figs.~\ref{fig:delta_ordPar_KCl_PCPS}, \ref{fig:delta_ordPar_NaCl_PCPS} 
and~\ref{fig:delta_ordPar_CaC_PCPS} as functions of KCl, NaCl or CaCl$_2$ concentrations,
and in Figs.~\ref{fig:delta_ordPar_NaCl_PC-PS_mix} as a function of PC and PS content. 
and in Figs.~\ref{OrderParameterCHANGESsurf} as a function of the content of dihexadecylammonium bromide, a cationic amphiphile.

\begin{figure}[tb!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/ecc_popc/PN_angle_OrdPars-A-B_L14-ECCL17_q80_sig89_surf.pdf} 
  \caption{\label{OrderParameterCHANGESsurf} 
    Changes of the head group order parameters $\alpha$, $\beta$ and P-N vector orientation as a function of 
    the molar fraction of a cationic surfactant dihexadecyldimethylammonium in a POPC bilayer 
    from simulations and experiments \citep{scherer89} at 313 K.
    Image reproduced from \cite{melcr18}.
  } 
\todo{Combine with Fig.~\ref{fig:delta_ordPar_NaCl_PC-PS_mix} into a single plot.} \\
\todo{SAMULI: I do not see any reason why we should show this data in this paper at all.}
\end{figure}

\begin{figure}[htb!] 
  \centering 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_nacl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_nacl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_kcl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_kcl.pdf} 
  \caption{\label{fig:delta_ordPar_NaCl_PC-PS_mix} 
    Changes of the head group order parameters of a POPC:POPS (5:1) bilayer as a function of PS content
    with \ce{Na^+} and \ce{K^+} counterions from simulations with ECC-lipids and Lipid17 \cite{lipid17-future} 
    and experiments (only \ce{Na^+} counterions). \cite{roux90}. 
    The underestimated response of ECC-lipids with \ce{Na^+} counterions 
    is likely due to a still slightly overestimated binding affinity of \ce{Na^+} to the phospholipids,
    which is corroborated by the series with \ce{K^+} counterions (lower affinity than \ce{Na^+}),
    where the response is closer to the experiment (which uses only \ce{Na^+} counterions). 
    Experimental points for POPS inherently contain larger systematic error, 
    as they come from independent experiments.
  } 
\todo{Josef: Simulation at 50:50 PC:PS might be useful for this plot (PC-PS interactions). 
Now it may make an impression, that we are consciously avoiding it. }
\end{figure}

>>>>

Changes of the lipid bilayer head group order parameters extracted from simulations and 
experiments \cite{roux90} are shown in Figs.~\ref{fig:delta_ordPar_KCl_PCPS}, \ref{fig:delta_ordPar_NaCl_PCPS} 
and~\ref{fig:delta_ordPar_CaC_PCPS} as functions of KCl, NaCl or CaCl$_2$ concentrations,
and in Figs.~\ref{fig:delta_ordPar_NaCl_PC-PS_mix} as a function of PC and PS content.

\begin{figure}[htb!] 
  \centering 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_nacl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_nacl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_kcl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_kcl.pdf} 
  \caption{\label{fig:delta_ordPar_NaCl_PC-PS_mix} 
    Changes of the head group order parameters of a POPC:POPS (5:1) bilayer as a function of PS content
    with \ce{Na^+} and \ce{K^+} counterions from simulations with ECC-lipids and Lipid17 \cite{lipid17-future} 
    and experiments (only \ce{Na^+} counterions). \cite{roux90}. 
    The underestimated response of ECC-lipids with \ce{Na^+} counterions 
    is likely due to a still slightly overestimated binding affinity of \ce{Na^+} to the phospholipids,
    which is corroborated by the series with \ce{K^+} counterions (lower affinity than \ce{Na^+}),
    where the response is closer to the experiment (which uses only \ce{Na^+} counterions). 
    Experimental points for POPS inherently contain larger systematic error, 
    as they come from independent experiments.
  } 
\end{figure}
